Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-03-08 manuscript 01/index.qmd
Update index.qmd

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical))
)

@@

# combine probability of OR > 1 (prob of difference)
prob_difference <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 1),
  "External Ventricular Drain" = pluck(evd, 1),
  "Tracheostomy" = pluck(trach, 1),
  "Days of Mechanical Ventilation" = pluck(vent, 1),
  "DNR Order" = pluck(dnr, 1),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 1),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 1)
)

# combine % of posterior within the ROPE
rope <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 4),
  "External Ventricular Drain" = pluck(evd, 4),
  "Tracheostomy" = pluck(trach, 4),
  "Days of Mechanical Ventilation" = pluck(vent, 4),
  "DNR Order" = pluck(dnr, 4),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 4),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 4)
)

@@

>>>>

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical))
)

@@

# combine probability of OR > 1 (prob of difference)
prob_difference <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 1),
  "External Ventricular Drain" = pluck(evd, 1),
  "Tracheostomy" = pluck(trach, 1),
  "Days of Mechanical Ventilation" = pluck(vent, 1),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 1),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 1),
  "DNR Order" = pluck(dnr, 1)
)

# combine % of posterior within the ROPE
rope <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 4),
  "External Ventricular Drain" = pluck(evd, 4),
  "Tracheostomy" = pluck(trach, 4),
  "Days of Mechanical Ventilation" = pluck(vent, 4),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 4),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 4),
  "DNR Order" = pluck(dnr, 4)
)

@@

ult_table <- t(ult_table)
```
